Region-network hierarchical sparsity priors for\\ high-dimensional inference in brain imaging

### 2016-01-24 paper/paper.tex
cosm

\section{Introduction}
% sparsity
Many quantitative scientific domains underwent a
recent passage from the classical regime (i.e., "long data")  to
the high-dimensional regime (i.e., "wide data")
\cite{jordan2015massive}.
Also in the brain imaging domain,
many contemporary methods for acquiring brain signals yield
more variables per observation than
total observations per data sample.
This high-dimensional scenario challenges many statistical estimators from
classical statistics.
For instance,
the general linear model without additional assumptions
yields an infinity of possible coefficients
and, thus, no solution.
%
Many such ill-posed estimation problems
have become tractable by means of
\textit{sparsity} assumptions
\cite{buhlmann2011statistics, hastie2015statistical}.
Sparsified supervised and unsupervised
learning algorithms have proven to yield
statistical relationships that can be readily
estimated, reproduced, and interpreted
\cite{giraud2014introduction}.
%
Further, \textit{structured sparsity} can impose
domain knowledge on the 
statistical estimation,
thus preassuming the variables to have unequal importance
and to obey expected data distributions
\cite{bach2012optimization}.
Yet, what neurobiological structure suggests itself
to harness the
\textit{curse of dimensionality} with
$\textgreater$100,000 variables
in neuroimaging research?

>>>>

\section{Introduction}
% sparsity
Many quantitative scientific domains underwent a
recent passage from the classical regime (i.e., ``long data")  to
the high-dimensional regime (i.e., ``wide data")
\cite{jordan2015massive}.
Also in the brain imaging domain,
many contemporary methods for acquiring brain signals yield
more variables per observation than
total observations per data sample.
This high-dimensional scenario challenges many statistical estimators from
classical statistics.
For instance,
the general linear model without additional assumptions
yields an infinity of possible coefficients
and, thus, no solution.
%
Many such ill-posed estimation problems
have become tractable by means of
\textit{sparsity} assumptions
\cite{buhlmann2011statistics, hastie2015statistical}.
Sparsified supervised and unsupervised
learning algorithms have proven to yield
statistical relationships that can be readily
estimated, reproduced, and interpreted
\cite{giraud2014introduction}.
%
Further, \textit{structured sparsity} can impose
domain knowledge on the 
statistical estimation,
thus preassuming the variables to have unequal importance
and to obey expected data distributions
\cite{bach2012optimization}.
Yet, what neurobiological structure suggests itself
to harness the
\textit{curse of dimensionality} with
$\textgreater$100,000 variables
in neuroimaging research?
